### 2014-03-26 paper/conclusion.tex
adding bjoern comments

\section{Conclusion}
While today's 3D printers are not yet able to fabricate active components in-place, we suggest that 3D printed interactive devices can be created with redirection of active input and output via tubes.  In addition to describing the design space of tubes and connecting related works created through both traditional processes and rapid prototyping methods, we also presented a design tool for the creation of tubes inside arbitrary 3D models.  We fabricated several example objects using this tool to explore new points in the design space.

>>>>

\section{Conclusion}

\bjoern{We should be more upfront in the paper that the particular sensing and actuation strategies we use are taken from prior work (for example wimmer's), but that there is still novelty in how we modify the models or redirect the input and output to different parts of the model with our pipe techniques. Otherwise I can see reviewers criticizing that we only show a collection of sensing techniques that have already been published.

it's important to frame that our techniques allow us to amplify and extend the utility of existing sensing and actuation approaches}

While today's 3D printers are not yet able to fabricate active components in-place, we suggest that 3D printed interactive devices can be created with redirection of active input and output via tubes.  In addition to describing the design space of tubes and connecting related works created through both traditional processes and rapid prototyping methods, we also presented a design tool for the creation of tubes inside arbitrary 3D models.  We fabricated several example objects using this tool to explore new points in the design space.

### 2014-03-26 paper/designspace.tex
add new figure to paper to illustrate types of pipes
adding bjoern comments

@@

Pipes need not have hollow centers: in the case where routed pipes are filled with solid material---in particular, a solid material different from the model material---, interactions such as those in \cite{Willis-printedoptics} are possible.

Particulates, either printed in-place or inserted, can be of varying densities.  A single particle can be used for display.  Sparse particles in a stream of fluid can provide haptic feedback.  Dense particles in a semi-closed pipe allow for jamming-based interactions at any point on the surface of an object \cite{Follmer-jamming}.

@@

Pipe designs may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toys}, where pipes must exit the toy at the frontal lobe, parietal lobes, etc.  An interface focused on the internal path of the pipe is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the pipe.

>>>>

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/types.png}
\caption{Types of pipes.  A shows a pair of open tubes filled with copper paint to power an LED.  B shows a return pipe with EL wire threaded through it.  C shows two semi-closed pipes with rubber membranes at their ends.  In D, a rabbit has a fully enclosed chamber to modify its weight.}
\label{fig:pipespace}
\end{figure}

@@

Pipes need not have hollow centers: in the case where routed pipes are filled with solid material---in particular, a solid material different from the model material---, interactions such as those in Printed Optics (\cite{Willis-printedoptics}) are possible.

Particulates, either printed in-place or inserted, can be of varying densities.  A single particle can be used for display.  Sparse particles in a stream of fluid can provide haptic feedback.  Dense particles in a semi-closed pipe allow for jamming-based interactions at any point on the surface of an object \cite{Follmer-jamming} \bjoern{may need more of an explanation.  you need jamming plus flexible surface material, right?}.

@@

\bjoern{Think of the ordering of dimensions is it a conscious choice to list this dimension last?}
Pipe designs may emphasize either their exterior features (connection points) or their interior paths.  These two features lead to different kinds of interfaces.  An example interface that focuses on the exterior connection points is the touch sensitive toy in Figure \ref{fig:toys}, where pipes must exit the toy at the frontal lobe, parietal lobes, etc.  An interface focused on the internal path of the pipe is the neon sign in Figure \ref{fig:neon}: output is based on the shape of the pipe.
